---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# dataspice

The goal of dataspice is to make it easier for researchers to create basic, lightweight and concise metadata files for their datasets. These basic files can then be used to:
- make useful information available during analysis.
- create a helpful dataset README webpage.
- produce more complex metadata formats to aid dataset discovery.

Metadata fields are based on [schema.org](http://schema.org/Dataset) and other metadata standards. 



## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ropenscilabs/dataspice")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

